\thesisTitle

### 2019-10-07 proposal/paper.tex
continued with the proposal

\usepackage{hyperref}

\usepackage[nameinlink]{cleveref}
\newcommand{\crefrangeconjunction}{--}

@@

@@

\section{Motivation}\label{sec:motivation}

@@

Since not all data is well-suited for a fixed-dimensional vector representation, approaches that directly consider the structure of the input data might be more appropriate in such cases.
One such case is the class of so-called \textit{``learning to aggregate''} (LTA) problems as described by \citet{Melnikov2016}.
There the instances are represented by compositions $\bm{c}$ of constituents $c_i \in \bm{c}$, i.e.\@ variable-size multisets.
The assumption in LTA problems is that for all constituents $c_i$ a local valuation $y_i \in \mathcal{Y}$ is either given or computable.
The set of those local valuations should be indicative of the overall valuation $y \in \mathcal{Y}$ of the entire composition $\bm{c}$.
The goal of LTA is to learn a variadic aggregation function $A: \mathcal{Y}^{*} \to \mathcal{Y}$ that estimates such composite valuations, i.e.\@ $\hat{y} = A(y_1, \dots, y_n)$ for a composition with $n$ constituents.
Additionally the aggregation function $A$ should be associative and commutative to fit with the multiset-structure of compositions.

\section{Related Work}\label{sec:related-work}

\section{Goals}\label{sec:goals}

\subsection{Required Goals}\label{sec:goals:req}

\subsection{Optional Goals}\label{sec:goals:opt}

\section{Approach}\label{sec:approach}

\section{Preliminary Document Structure}\label{sec:doc-structure}

@@

\section{Time-Schedule}\label{sec:schedule}

>>>>

\usepackage{hyperref}
\usepackage[nameinlink]{cleveref}
\newcommand{\crefrangeconjunction}{--}

@@

\usepackage[inline]{enumitem}

@@

\section{Motivation}%
\label{sec:motivation}

@@

Since not all data is well-suited for a fixed-dimensional vector representation, approaches that directly consider the structure of the input data might be more appropriate in such cases.
One such case is the class of so-called \textit{learning to aggregate} (LTA) problems as described by \citet{Melnikov2016}.
There the instances are represented by compositions $\bm{c}$ of constituents $c_i \in \bm{c}$, i.e.\@ variable-size multisets.
The assumption in LTA problems is that for all constituents $c_i$ a local valuation $y_i \in \mathcal{Y}$ is either given or computable.
The set of those local valuations should be indicative of the overall valuation $y \in \mathcal{Y}$ of the entire composition $\bm{c}$.
The goal of LTA is to learn a variadic aggregation function $A: \mathcal{Y}^{*} \to \mathcal{Y}$ that estimates such composite valuations, i.e.\@ $\hat{y} = A(y_1, \dots, y_n)$ for a composition with $n$ constituents.
Additionally the aggregation function $A$ should be associative and commutative to fit with the multiset-structure of compositions.

Current LTA approaches only work with multiset inputs.
In practice there is however often some relational structure among the constituents of a composition.
This effectively turns LTA into a graph classification or regression problem.
The overall aim of this thesis is to look into the question of how aggregation function learning methods might be generalized to the graph setting.

\section{Related Work}%
\label{sec:related-work}

This thesis will be based on two currently mostly unrelated fields of research:
\begin{enumerate*}
	\item Aggregation function learning
	\item Graph classification
\end{enumerate*}.
A short overview of the current state-of-the-art approaches in both fields will be given now.

\subsection{Aggregation Function Learning}%
\label{sec:related-work:lta}

\subsection{Graph Classification}%
\label{sec:related-work:gc}

\section{Goals}%
\label{sec:goals}

\subsection{Required Goals}%
\label{sec:goals:req}

\subsection{Optional Goals}%
\label{sec:goals:opt}

\section{Approach}%
\label{sec:approach}

\section{Preliminary Document Structure}%
\label{sec:doc-structure}

@@

\section{Time-Schedule}%
\label{sec:schedule}
